%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\usepackage{CJKutf8}

\begin{document}
\header{scott}{crooks}
       {engineer and project manager}


% In the aside, each new line forces a line break
\begin{aside}
  \section{address}
    4th Floor, No. 26
    Alley 27, Lane 55
    Section 1, Xinglong Road
    Wenshan District
    Taipei City, Taiwan 116
  \section{mobile}
    +886 978 788 646
  \section{links}
    \href{mailto:scott.crooks@gmail.com}{scott.crooks@gmail.com}
    \href{http://linkedin.com/in/jshcrooks}{linkedin://jshcrooks}
    \href{http://facebook.com/scott.crooks}{facebook://scott.crooks}
    \href{http://github.com/sc250024}{github://sc250024}
  \section{languages}
    English (native)
    Mandarin Chinese (working proficiency)
  \section{programming}
    {\color{red} $\varheartsuit$} BASH / Shell
    Python, PHP
    SQL \& \LaTeX
\end{aside}

\section{interests}

entrepreneurship, chinese language and culture, coding / hacking events, public speaking, typography, graphic design, theoretical physics

\section{education}

\begin{entrylist}
  \entry
    {2014-2015}
    {International Chinese Language Program}
    {National Taiwan University}
    {\emph{Nine months of intensive Mandarin Chinese studies.}}
  \entry
    {2004–2009}
    {B.Sc. Cum laude}
    {Oregon State University}
    {Majoring in Chemical Engineering\\
    \emph{Specialization in Material Sciences and Engineering}}
\end{entrylist}

\section{work experience}

\begin{entrylist}

  \entry
    {2011-2014}
    {MCON China Ltd. // Beijing, China}
    {Engineering Team Leader / Senior Systems Engineer}
    {\emph{- Consulting for German automotive companies in Beijing in the areas of system architecture, project management, and code deployment.\\
    - Managed a team of 5 engineers, supervising daily engineering duties, as well as ensuring proper training for members of the team.\\
    - Learned our company’s infrastructure in Germany, China, India, and South Korea, within the period of 12 months; afterwards was able to manage tasks in our Beijing datacenter.\\
    - Created training courses, created screencasts and technical manuals for our teams in China and Germany.}}

  \entry
    {2011-2011}
    {ChinaSoft DK // Beijing, China}
    {Project Leader}
    {\emph{Managed 4 web development projects during my tenure for 3 different clients in Denmark in the newsprint media, healthcare, and a consumer-to-consumer (C2C) industries.\\
    - Quality testing on developed code based on customer requirements.\\
    - Quickly gained knowledge of the Drupal content management system, coded modules to enhance learning of the Drupal system.}}

\end{entrylist}

\section{special skills}

\begin{itemize}
\item
Great at writing technical documents and standards, as well as creating screencasts for more technically challenging topics.
\item
Advanced knowledge in server and network infrastructure monitoring using latest open-source solutions.
\item
Capable of learning complex systems quickly as a result of my chemical engineering background.
\item
Skilled at engineering deployment solutions for code developers using Git and Jenkins, specifically for Java-based Maven builds.
\item
Firm understanding of the business culture in China, and able to assist a company’s entry into the Chinese market.
\end{itemize}

\end{document}
